\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-09 doc/paper.tex
Future work revision, combining two paragraphs.

	\subsection{Informative Qualification} As we found in the case study, the tool
	excels at making formula examples available throughout a tree. 	
	However, the benefits described in the previous sections imply a hidden
	complication: if the tool educates through example but does not explicitly
	distinguish between good design and bad design, how can we be sure that people
	will not inadvertently learn bad design from it? In the user study, we
	discussed its use in education and smell detection by bringing up the issues
	surrounding the LOOKUP functions; this discussion, though, presupposes a
	distinguishing eye that knew which examples practiced good design and which
	exhibited the common errors. A beginner might not know the difference.
	Robillard and Deline, in their study, remarked that good API examples should
	demonstrate best practices, but, right now, we have no way to assure this with
	\toolnameend. As with the problems in achieving unbiased exploration, correcting
	for this danger may entail a reevaluation of design goals.

	\section{Future Work} For these user and case studies, we relied solely on
	Enron's spreadsheets. However, Enron's focus on finances and energy represents
	only one context in which people use spreadsheets. Other corpora, like EUSES
	and Fuse, draw from other domains and industries, and, as Jansen found in his
	comparison of spreadsheets Enron and EUSES \cite{jansen2015enron}, different
	companies rely on different functions. Though the use of a single corpora
	nevertheless suffices for evaluation, we may yet be able to find more
	interesting applications and uses for the tool in other types of spreadsheet.
	\par

	Additionally, Excel is only one of many different spreadsheet products
	available, chosen for this project because of its prevalence. But other
	spreadsheets, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
	Sheets\footnote{https://www.google.com/sheets/about/} represent other
	approaches to spreadsheet systems. Even within identical domains, there's no
	guarantee that practices and functions will hold across these varied offerings.
	This, then, warrants further analysis, in which good visualization might serve
	well. \par

@@

	%\begin{wrapfigure}{O}{.25\textwidth} \centering
	%	\includegraphics[width=.25\textwidth]{longIF} \label{fig:longif} \caption{The
	%		many possibilities of IF, argument 3, demonstrate the problem of having too
	%		many options.} \end{wrapfigure}

	\section{Conclusion} This paper presents a tool to support the exploration of
	function combinations throughout a given spreadsheet dataset. By taking an
	agnostic approach to design quality, it attempts to convey the dataset's
	spreadsheet practices as is: the common along with the anomalous, and the
	well-designed along with the odorous. As seen in the user and case studies,
	this allows it to take on several potential roles at once, such as an
	environment for investigating code smells as well as a repository for examples
	for learning new techniques. \par

@@

	% use section* for acknowledgment
	\section*{Acknowledgment} This material is based upon work supported in whole
	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
	opinions, findings, conclusions, or recommendations expressed in this material
	are those of the author(s) and do not necessarily reflect the views of the LAS
	and/or any agency or entity of the United States Government. I also thank the
	anonymous reviewers who advised the direction of this paper.

>>>>

	\subsection{Informative Qualification}

	As we found in the case study, the tool excels at making formula examples
	available throughout a tree. However, the benefits described in the previous
	sections imply a hidden complication: if the tool educates through example but
	does not explicitly distinguish between good design and bad design, how can we
	be sure that people will not inadvertently learn bad design from it? In the
	user study, we discussed its use in education and smell detection by bringing
	up the issues surrounding the LOOKUP functions; this discussion, though,
	presupposes a distinguishing eye that knew which examples practiced good design
	and which exhibited the common errors. A beginner might not know the
	difference. Robillard and Deline, in their study, remarked that good API
	examples should demonstrate best practices, but, right now, we have no way to
	assure this with \toolnameend. As with the problems in achieving unbiased
	exploration, correcting for this danger may entail a reevaluation of design
	goals.

	\section{Future Work}

	For these user and case studies, we relied solely on one type of spreadsheet (Excel)
	from one source (Enron), but we have room to develop in either dimension. For sources, 
	Enron's focus on finances and energy represents one context in
	which people use spreadsheets, but other corpora, like EUSES and Fuse, draw from
	other domains and industries. As Jansen found in his comparison of
	spreadsheets Enron and EUSES \cite{jansen2015enron}, different companies rely
	on different functions. For other types of spreadsheet, such as Gnumeric\footnote{http://www.gnumeric.org/} or Google
	Sheets\footnote{https://www.google.com/sheets/about/}, we have no
	guarantee that practices and functions will hold across these varied programs, even within
	similar domains. This, then, warrants further analysis, in which good visualization might serve
	well. \par

@@

	\section{Conclusion}

	This paper presents a tool to support the exploration of function combinations
	throughout a given spreadsheet dataset. By taking an agnostic approach to
	design quality, it attempts to convey the dataset's spreadsheet practices as
	is: the common along with the anomalous, and the well-designed along with the
	odorous. As seen in the user and case studies, this allows it to take on
	several potential roles at once, such as an environment for investigating code
	smells as well as a repository for examples for learning new techniques. \par

@@

	% use section* for acknowledgment
	\section*{Acknowledgment}

	This material is based upon work supported in whole or in part with funding
	from the Laboratory for Analytic Sciences (LAS). Any opinions, findings,
	conclusions, or recommendations expressed in this material are those of the
	author(s) and do not necessarily reflect the views of the LAS and/or any agency
	or entity of the United States Government. I also thank the anonymous reviewers
	who advised the direction of this paper.
